---
output:
  pdf_document: default
  html_document: default
---
```yaml
---
title: "Multiple Binary Logistic Regression"
author: "Izan Khan"
date: "`r format(Sys.Date(), '%B %d, %Y')`"
output:
  pdf_document:
    number_sections: true
    toc: true
    fontsize: 11pt
    geometry: margin=1in
---
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This markdown file utilizes multiple binary logistic regression, using "rejected" as the reference variable

```{r data, include=FALSE}
# Load data
ucb <- as.data.frame(UCBAdmissions)
head(ucb)
```

## Estimate odds ratio and 95% confidence interval for predictor variables, relative to the reference variable ("Rejected")

```{r logistic}
# Example: Multiple Binary Logistic Regression
model1 <- glm(Admit ~ Gender + Dept, family = binomial, data = ucb, weights = Freq)
summary(model1)
exp(cbind(OR = coef(model1), confint.default(model1)))
```

## We see that GenderFemale and Dept B do not appear to be significant predictors, as 1 lies within their confidence intervals, which indicates they are not statistically significant. Their odds ratios are near 1, which means these have a small effect

```{r predicted probability}
ucb$pred_prob <- predict(model1, type = "response")
head(ucb)

library(ggplot2)

ggplot(ucb, aes(x = Dept, y = pred_prob, color = Gender)) +
  geom_point(size = 3) +
  labs(y = "Predicted Probability of Admission")
```